### 2020-02-04 paper/revisions/review-responses.tex

        \begin{solution}
                Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
        \end{solution}

        %---------------------------------------------------------------------

        \question SD-TMSR concept development does not correctly described in the section "introduction", where it states that the SD-TMSR was introduced by the Chinese Academy of Sciences. Actually, SD-TMSR concept was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) (see Ref.: Tech. Rep. ORNL-4541). In addition, the study of reference 7 which was cited to illustrate SD-TMSR concept actually adopted the single-flow single-zone MSR rather than SD-TMSR.

        \begin{solution}
                 Thank you for catching this. The whole statement has been modified to read:\\
                 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
                 MW$_{th}$ was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.

                 Thank you for catching this. Reference 7 has been removed from the paragraph.

@@

        \end{solution}

        %---------------------------------------------------------------------

        \question The authors did not conduct a sufficient literature survey on the fuel cycle transition studies for the SD-TMSR concept. Cui. et al., have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) (see Ref.: Transition toward thorium fuel cycle in a molten salt reactor by using plutonium, NUCL SCI TECH (2017) 28:152; Possible scenarios for the transition to thorium fuel cycle in molten salt reactor by using enriched uranium. Progress in Nuclear Energy 104 (2018) 75-84). The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except U-233) has not studied before" in page 3 is therefore inaccurate.
        \begin{solution}
                Thank you for your helpful review. The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except$^{233}$U) has not studied before" in page 3, has been removed.

                Also, the mentioned references have been added as following:\\
                Cui \emph{et al.} (2017-2018) have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) \cite{cui2017transition,cui2018possible}.

@@

        \end{solution}

        %---------------------------------------------------------------------

        \question More details should be provided to illustrate the heavy metal addition for the thorium feed mechanism and non-thorium feed mechanism in page 11. It is hard to understand why the mass of Th / external heavy metals (excluding Th) is approximately equal to the mass of extracted Pa.
        \begin{solution}
               Thank you for the comment. Actually, in page 11, we mention that the mass of Th / external heavy metals (excluding Th) is approximately equal to the mass of extracted Fission products (FPs) and not Pa. Because in both feed mechanisms (thorium and non-thorium) we continually added $^{233}$U and the mass of$^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decay to $^{233}$U after $\approx$ 27 d). To keep the total fuel mass almost constant, the mass of Th/ external heavy metals (excluding Th) must be equal to the mass of extracted FPs. 
               Moreover, we rewrite the paragraph in page 11 to address this thought:\\
               \begin{enumerate}
               	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
               	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
               	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
               	\subitem 3a. \textbf{Thorium feed mechanism}: mass of $^{233}$U $\approx$ mass of extracted Pa and mass of Th $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
               	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of $^{233}$U $\approx$ mass of extracted Pa and mass of heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, TRU) $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
               	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
               \end{enumerate}

### 2020-02-04 paper/introduction.tex
solve issue #35

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
MW$_{th}$ was introduced by the Chinese Academy of Sciences \cite{li_optimization_2018}. The
SD-TMSR
is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U
fuel cycle. In the SD-TMSR, the fissile and fertile elements are integrated
into a single salt. To improve the breeding ratio, the active core is divided into two zones:
the radius of the fuel channels in the outer zone is modified to be larger
than the radius of the fuel channels in the inner zone \cite{nuttin2005potential,li_optimization_2018}.

@@

Betzler \emph{et al.} (2016) discussed the simulation of the startup of a \gls{MSBR} unit
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent nuclear fuel (SNF) as initial
fissile materials \cite{betzler2016modeling}. They concluded that the 
Pu vector extracted from LWR SNF is the best alternative source to 
$^{233}$U because it has a high ratio of fissile isotopes
\cite{betzler2016modeling}. Zou \emph{et al.} (2018) introduced two approaches for
the thorium fuel cycle transition in the \gls{TMSR}: (1) in-core transition and 
(2) ex-core transition. In the first approach, the TMSR is launched with 
existing fissile material and thorium as a fertile material; then the 
$^{233}$U bred from thorium is rerouted into the core to maintain criticality. 
In contrast, the second approach tends to store produced $^{233}$U out of the 
core until there is enough to start a new TMSR \cite{zou2018transition}.
Zou \emph{et al.} (2018) studied the transitioning to thorium fuel
cycle in a small modular Thorium-based Molten Salt Reactor (smTMSR) using \gls{TRU}
as startup fuel. They concluded that the transition to a thorium fuel cycle can
be achieved in a thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.

@@

Various previous works explore starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many such publications have focused on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	fiorina2013investigation}, while few focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
	zou2018transition,zou2018preliminary}. For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other
fissile materials (except $^{233}$U) has not been studied before. Therefore,
the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the \gls{SD-TMSR} with
various initial fissile materials and without any external feed of $^{233}$U. We investigate five different
initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu \footnote{Reactor-grade Pu is a mixture of Pu isotopes chemically extracted from PWR SNF with 33 GWd/tHM burnup} \cite{marka1993explosive}, \gls{TRU} from LWR SNF \cite{de2000scenarios}, and $^{233}$U. Two different feed mechanisms were selected:

>>>>

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
MW$_{th}$ was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.
The SD-TMSR is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U
fuel cycle. In the SD-TMSR, the fissile and fertile elements are integrated
into a single salt. To improve the breeding ratio, the active core is divided into two zones:
the radius of the fuel channels in the outer zone is modified to be larger
than the radius of the fuel channels in the inner zone \cite{li_optimization_2018}.

@@

Betzler \emph{et al.} (2016) discussed the simulation of the startup of a \gls{MSBR} unit
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent nuclear fuel (SNF) as initial
fissile materials \cite{betzler2016modeling}. They concluded that the 
Pu vector extracted from LWR SNF is the best alternative source to 
$^{233}$U because it has a high ratio of fissile isotopes
\cite{betzler2016modeling}. Zou \emph{et al.} (2018) introduced two approaches for
the thorium fuel cycle transition in the \gls{TMSR}: (1) in-core transition and 
(2) ex-core transition. In the first approach, the TMSR is launched with 
existing fissile material and thorium as a fertile material; then the 
$^{233}$U bred from thorium is rerouted into the core to maintain criticality. 
In contrast, the second approach tends to store produced $^{233}$U out of the 
core until there is enough to start a new TMSR \cite{zou2018transition}.

Cui \emph{et al.} (2017-2018) have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) \cite{cui2017transition,cui2018possible}.

Zou \emph{et al.} (2018) studied the transitioning to thorium fuel
cycle in a small modular Thorium-based Molten Salt Reactor (smTMSR) using \gls{TRU}
as startup fuel. They concluded that the transition to a thorium fuel cycle can
be achieved in a thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.

@@

Various previous works explore starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many such publications have focused on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	fiorina2013investigation}, while few focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
	zou2018transition,zou2018preliminary}. Therefore,
the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the \gls{SD-TMSR} with
various initial fissile materials and without any external feed of $^{233}$U. We investigate five different
initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu \footnote{Reactor-grade Pu is a mixture of Pu isotopes chemically extracted from PWR SNF with 33 GWd/tHM burnup} \cite{marka1993explosive}, \gls{TRU} from LWR SNF \cite{de2000scenarios}, and $^{233}$U. Two different feed mechanisms were selected:
